---
title: "p8105_hw1_kl3181"
author: "Kelley Lou"
date: 2020-09-25
output: github_document
---

## Problem 1
Creating a data frame comprised of a random sample of size 10 from a normal distribution, a logical vector, a character vector length of 10 and a factor vector length of 10 with 3 levels.
```{r}
library(tidyverse)
```

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```
I can take the mean of numbers and logical but not character or factor. 

Now converting the variables into numeric.
```{r try_numeric, eval=FALSE}
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
When the variables are converted into numeric, the factors levels are converted into numbers. This explains why you cannot take the mean when the levels have not been converted into numbers yet. 

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```
Converting the logical into a factor and multiplying the result by the sample results in an error but when the factor is then converted into numeric, then we are able to get a result.


## Problem 2
```{r}
data("penguins", package = "palmerpenguins")
mean(as.numeric(pull(penguins, flipper_length_mm)), na.rm = TRUE)
```
The penguins data set has 8 variables, including species, island, bill length, bill depth, flipper length, body mass, sex and study year. There are `r nrow(penguins)` rows and `r ncol(penguins)` columns of data. A key variable is the species, which consists of three "levels" including Adélie, Chinstrap and Gentoo. The bill length (mm), bill depth (mm), flipper length (mm) and body mass (g) are all numeric values. The mean flipper length is 200.9152 mm. 

Making a scatterplot of flipper length on the y axis and bill length on the x axis. 
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf", height = 6, width = 4)
```

